A Switching Planner for Combined Task and Observation Planning

### 2010-11-24 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/dtpddl.tex
NOt more "blocks". Also, I got rid of the ambiguity with uninitialised variables.

The modelling language of choice for planning in probabilistic
problems is the Probabilistic Planning Domain Definition
Language~\cite{younes:littman:04,younes:etal:2005}. PPDDL was used in
all 3 of the International Planning Competitions since 2004. A
variation on PDDL for describing domains with stochastic actions and
uncertain starting configurations, PPDDL is a declarative first-order
(a.k.a., relational) language that facilitates factored description of
domains and problem instances. There are straightforward compilations
from problems expressed compactly in PPDDL to propositional
representations amenable to state-of-the-art planning procedures.

Because PPDDL cannot model domains that feature partial observability,
we developed an extension of that language, called DTPDDL. This can
express probabilistic models of the sensing consequences of acting, to
quantitatively capture unreliability in perception. That expressive
power is achieved by incorporating perceptual analogues of fluent,
predicate, and action definitions. In detail, we have declarations of
state characterising predicate and fluent symbols according to the
PPDDL syntax. In addition, we allow two other declarative blocks, for
perceptual predicates and fluents respectively. For example, suppose
our robot is tasked with exploring {\em locations} in order to
identify the whereabouts of a {\em visual-object}. We must describe
state and perceptual facts that model the {\em true}, resp. perceived,
locations of objects. In DTPDDL, these declarations appear as:

@@

\noindent In a slight departure from PPDDL, we suppose that
$\pp{look-for-object}$ has an effect on the state. That is, its
execution incurs a penalty, $3$, corresponding to the {\em cost} of
performing the visual search.\footnote{In PPDDL {\em reward} is a {\em
reserved word}, and occurs in {\em increased} and {\em decreased}
clauses of operator schemata. In that setting, {\em reward} is
interpreted as accumulated (resp. instantaneous) rewards and
penalties.}

@@

\noindent Here, the {\em execution} clause is a lifted description of
the sense action-precondition -- I.e,
$(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office}) =
\poss_\stochActions(\pp{vision}~\pp{DORA}~\pp{box}~\pp{office})$. Above,
we include a redundant state-precondition, $(=(\pp{is-in}~?r)?l)$ in
order to fully demonstrate the syntax. Interpreting the above schema,
if action $(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office})$ is
executed, there is a $0.8$ chance of perceiving the box if it is in
the $\pp{office}$, and otherwise a $0.1$ of perceiving it.

>>>>

The modelling language of choice for planning in probabilistic
problems is the Probabilistic Planning Domain Definition
Language~\cite{younes:littman:04,younes:etal:2005}. PPDDL was used in
all 3 of the International Planning Competitions since 2004. A
variation on PDDL for describing domains with stochastic actions and
uncertain starting configurations, PPDDL is a declarative first-order
language that facilitates factored description of domains and problem
instances. There are straightforward compilations from problems
expressed compactly in PPDDL to propositional representations amenable
to state-of-the-art planning procedures.

Because PPDDL cannot model domains that feature partial observability,
we developed an extension of that language, called DTPDDL. This can
express probabilistic models of the sensing consequences of acting, to
quantitatively capture unreliability in perception. That expressive
power is achieved by incorporating perceptual analogues of fluent,
predicate, and action definitions. In detail, we have declarations of
state characterising predicate and fluent symbols according to the
PPDDL syntax. In addition, we allow two other declarations, for
perceptual predicates and fluents respectively. For example, suppose
our robot is tasked with exploring {\em locations} in order to
identify the whereabouts of a {\em visual-object}. We must describe
state and perceptual facts that model the {\em true}, resp. perceived,
locations of objects. In DTPDDL, these declarations appear as:

@@

\noindent In a slight departure from PPDDL, we suppose that
$\pp{look-for-object}$ has an effect on the state. That is, its
execution incurs a penalty, $3$, corresponding to the {\em cost} of
performing the visual search.\footnote{In PPDDL {\em reward} is a {\em
reserved word}, and occurs in {\em increased} and {\em decreased}
terms in operator schemata. In that setting, {\em reward} is
interpreted as accumulated (resp. instantaneous) rewards and
penalties.}

@@

\noindent Here, the {\em execution} declaration is a lifted description of
the sense action-precondition -- I.e,
$(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office}) =
\poss_\stochActions(\pp{vision}~\pp{DORA}~\pp{box}~\pp{office})$. Above,
we include a redundant state-precondition, $(=(\pp{is-in}~?r)?l)$ in
order to fully demonstrate the syntax. Interpreting the above schema,
if action $(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office})$ is
executed, there is a $0.8$ chance of perceiving the box if it is in
the $\pp{office}$, and otherwise a $0.1$ of perceiving it.

### 2010-11-24 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
New section
NOt more "blocks". Also, I got rid of the ambiguity with uninitialised variables.

\section{Discussion and Related Work}
\input{discussion.tex}

@@

The planner has a compulsory starting action, that visits the root
term, and then has to execute visitation actions until that plan
prefix corresponds to a valid {\em abstract visitation} of the {\em
:init} block. Beyond such a prefix, the process actions and senses are
available to the planner

>>>>

%% \section{Discussion}
%% \input{discussion.tex}

\section{Related Work}
\input{relatex.tex}

@@

The planner has a compulsory starting action, that visits the root
term, and then has to execute visitation actions until that plan
prefix corresponds to a valid {\em abstract visitation} of the {\em
:init} decleration. Beyond such a prefix, the process actions and senses are
available to the planner
